Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)

### 2024-04-18 paper/paper.qmd
upload paper.qmd and llm usage2

---
title: "Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)"
author: "Jagpreet Singh"
thanks: "Code and data are available at: https://github.com/Jagpreet5ingh/female_fertility_rate_south_asia.git"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
date-format: long
bibliography: references.bib
execute: 
  echo: false
format: pdf
fig-pos: "H"
abstract: This paper utilizes data from the World Bank’s Gender Statistics database to examine the relationship between the adult female literacy rate (% of females ages 15 and above) and fertility rate (total births per woman) in South Asia between 2000-2020. The analysis revealed a negative correlation between the two variables, indicating that as the literacy rate increased, the fertility rate decreased. These findings matter as they highlight the importance of investing in female education and empowerment to manage population growth and promote sustainable development. The insights can guide policymakers make decisions on education initiatives and reproductive health programs to further enhance socioeconomic progress in the region.
---
```{r}
knitr::opts_chunk$set(echo = FALSE, results ="hide", message = FALSE, warning = FALSE)
```
```{r}
#| include: false
#| warning: false
#| message: false

@@

# Data {#sec-data}

```{r, results='asis'}
#| echo: false
#| warning: false
#| label: tbl-data
#| tbl-cap: "A summary table of cleaned data"

@@

```
## Data Source {#sec-variables-of-interest}

@@

>>>>

---
title: "Books and Babies: An Analysis of the Relationship between Female Literacy Rate and Fertility Rate in South Asia (2000-2020)"
author: "Jagpreet Singh"
thanks: "Code and data are available at: https://github.com/Jagpreet5ingh/female_fertility_rate_south_asia.git"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
date-format: long
bibliography: references.bib
execute: 
  echo: false
format: pdf
fig-pos: "H"
abstract: This paper utilizes data from the World Bank’s Gender Statistics database to examine the relationship between the adult female literacy rate (% of females ages 15 and above) and fertility rate (total births per woman) in South Asia between 2000-2020. The analysis revealed a negative correlation between the two variables, indicating that as the literacy rate increased, the fertility rate decreased. These findings matter as they highlight the importance of investing in female education and empowerment to manage population growth and promote sustainable development. The insights can guide policymakers make decisions on education initiatives and reproductive health programs to further enhance socioeconomic progress in the region.
---
```{r}
knitr::opts_chunk$set(echo = FALSE, results ="hide", message = FALSE, warning = FALSE)
```

@@

# Data

## Data Description and Methodology
```{r}
#| include: false
#| warning: false
#| message: false

```
```{r, results='asis'}
#| echo: false
#| warning: false
#| label: tbl-data
#| tbl-cap: "A summary table of cleaned data"

@@

## Data Visualization

### Trend of Female Literacy Rate in South Asia (2000-2020)

```{r fig.width=12, fig.height=8}
#| label: fig-1
#| fig-cap: literacy rate, adult females (% of females ages 15 and above) in South Asia (2000-2020) 
#| echo: false
#| warning: false
# Load necessary libraries
library(ggplot2)
library(here)

# Read data from CSV file
analysis_data <- read.csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))

# Create ggplot
ggplot(data = analysis_data, aes(x = Year, y = female_literacy_rate)) +
  geom_line(color = "dark green") +  # Change to line graph
  labs(x = "Year", y = "Female Literacy Rate (% of females ages 15 and above)")
```

### Trend of Fertility Rate in South Asia (2000-2020)

```{r fig.width=12, fig.height=8}
#| label: fig-2
#| fig-cap: literacy rate, Fertility Rate, Total (births per woman) in South Asia (2000-2020) 
#| echo: false
#| warning: false
# Load necessary libraries
library(ggplot2)
library(here)

# Read data from CSV file
analysis_data <- read.csv(here::here("data/analysis_data/cleaned_data_south_asia_2000_2020.csv"))

# Create ggplot
ggplot(data = analysis_data, aes(x = Year, y = fertility_rate_total)) +
geom_line(color = "red") +  # Change to line graph
  labs(x = "Year", y = "Fertility Rate, Total (births per woman)")
```

@@

```{r, results='asis'}
#| label: tbl-model
#| tbl-cap: "T-Value and P-Value of Regression"
#| echo: false
#| warning: false
library(knitr)

library(modelsummary)

loaded_model <- readRDS(here::here("models/linear_model.rds"))

model_summary <- summary(loaded_model)

t_values <- model_summary$coefficients[, "t value"]
p_values <- model_summary$coefficients[, "Pr(>|t|)"]

summary_df <- data.frame(t_value = t_values, p_value = p_values)
kable(summary_df)
```
